SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-13 frontrunning/Latex/sections/paper.tex
some minor edits

As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks. Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack. A particular system may implement more in a layered mitigation approach.

@@

One alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin does not have a front-running problem for most standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

Finally, transactions themselves could enforce order. In particular, they could point to the current state of the contract and only execute on that exact state. This transaction chaining only prevents certain sub-types of front-running. For example, it could prevent scalping attacks: if Alice buys from a marketplace that matches her order to Bob with a price improvement, a miner could buy from Bob first and then execute Alice's original transaction which results in her being matched to Alice instead. By contrast, if Alice registers an interesting-looking domain name, transaction chaining does not stop a miner from replacing Alice's request with her own. Transaction chaining would likely lead to more orphaned transactions for active contracts, as only one state-changing transaction would be allowed per state.

>>>>

As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks. Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack. A particular system may implement more than one in a layered mitigation approach.

@@

One alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin does not have a front-running problem for standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

Finally, transactions themselves could enforce order. For example, they could specify the current state of the contract as the only state to execute on. This transaction chaining only prevents certain types of front-running; \ie it prevents insertion attacks but not displacement attacks (recall our taxonomy in Section~\ref{sec:taxonomy}). As transaction chaining only allows one state-changing transaction per state, at most one of a set of concurrent transactions can be confirmed.
